\section{experience}

\begin{entrylist}
  \entry
    {2020}
    {Vice President, Technology}
    {Calgary, Canada}
    {
      \textbf{DC Bank}
      \begin{itemize}
        \item Lead IT and set vision for growth 
      \end{itemize}
    }
  % monahees+
  % codenation
  % handson
  \entry
  \entry
    {2020}
    {Senior Manager, IT Airline Operations}
    {Toronto, Canada}
    {
      \textbf{Air Canada Airlines}
      \begin{itemize}
        \item Managed all flight operations applications 
	\item Secured funding and project managed move of critical application to the AWS Cloud 
      \end{itemize}
    }
  % monahees+
  % codenation
  % handson
  \entry
    {2012-2019}
    {Manager, IT Airline Operations}
    {Calgary, Canada}
    {
      \textbf{WestJet Airlines}
      \begin{itemize}
        \item Led leaders in flight operations, flight technical and digital areas. 
        \item Led the move of all flight operations tools to digital platforms.
        \item Led efforts to establish continious delivery pipeline of digital tools using Xcode, Github and internal tools. 
        \item Created executive dashboards to highlight revenue and loyalty opportunities for airline passengers.  
        \item Led efforts to build API's and standardize reporting for all internal customers consuming airline operation statistics. 
        \item Launched IT systems for two airlines - Swoop and WestJet Encore.
        \item Moved ecommerce plafform from Windows to Linux, and then to the cloud.
        \item Created automated release pipeline for whole ecommerce platform. 
        \item Responsible for ensuring the performance, stability and scalability of all IT systems required for flight operations. 
      \end{itemize}
    }
  \entry
    {2006-2012}
    {Senior Systems Architect}
    {Los Angeles, California}
    {
      \textbf{University of Southern California}
      \begin{itemize}
        \item Built multi-petabyte in perpetuity archive for the Shoah Foundations video testimonies, with  over half a million videos. 
        \item Built and maintained the main teaching portal at the University.
        \item Contributed to Internet2 peering standards, and collaborated on performance tuning of PacWave cables, connecting North America with Oceania.
        \item Built the university's fiber channel SAN network.
      \end{itemize}
    }
  \entry
    {2004-2006}
    {IT Generalist}
    {Century City, California}
    {
      \textbf{ForestWeb}
      \newline
     Managed all IT functionality for publishing startup, including setup of servers, Database configuration, Development, and Email.
      % \begin{itemize}
      % \end{itemize}
    }
\end{entrylist}
